% Should make this into a real Latex file at some point for better formatting.


ExtractModel discussions:


1) Find all Input, External, Constraint and Cost BLOM library blocks.
2) Build cost and constraint dependency wire graph, starting from Constraint and Cost blocks and traverse backwards.
    a)  BFS to find the graph.
    b)  Recognize reaching non-BLOM inputs (user error).
    c)  Format of the graph: Sparse connectivity matrix of all wires, 
        store just the block handles.
    d)  Each wire has a property whether optimization variables is
            introduced for it for each derivative evaluation, 
        intermediate major time step, initial time, final time.
    e)  Store for each wire, if it is constrained, cost (discrete or continuous), 
        input, external.
3) Flatten the wires:
    a)  "Fetch" all PolyBlocks data: variables from the base workspace 
        or values from the dialog (just do evalin('base',get_param(h,'A')).
    b)  Get all possible dimensions from the known PolyBlocks (with or without the Simulink "compile").
    c)  Translate all supported Simulink blocks to PolyBlocks using the known dimensions.   
    d)  Eliminate duplicate routing variables. 
    e)  Combine all PolyBlocks to a large P and K matrices.
    f)  Eliminate whatever is possible (constants, identity PolyBlocks, linearly dependent constraints, replicated P rows, unused terms).
    g)  Propagate time property information using the processed P and K structure.    
4) Create the whole problem:
    a)  Introduce and duplicate all major time step variables, including their dependencies.
    b)  Introduce and duplicate minor time steps variables and their dependencies.
    c)  Link by the appropriate Butcher tableau values major and minor time steps variables.
    d)  Add move blocking constraints.
    e)  Eliminate whatever is possible.
    f)  Mark external, input.
    g)  Take care of cost.



%%%%%%%%%%%%%%%%%%%%%%%%%%

Tony's folder structure ideas:

Only put a handful of files in the base directory. An addpath script, a quickstart guide, any license/authors/etc stuff needed for distribution.

The Simulink library (which should have a better name - how about BLOM_Sim_Lib.mdl?) and really important functions like BLOM_ExtractModel should be under Core (or some other "hey! important stuff is in here!" name)

Docs, Examples, and Solvers are pretty self-explanatory. I was brainstorming about possible solvers we have thought about making interfaces for, maybe putting empty folders as notes will be good motivation :)
The common folder under Solvers is for useful libraries/utilities like SparseLib++ that we might use across multiple solver interfaces.

Utils should be things like BLOM_ConvertStructToVector and BLOM_ConvertVectorToStruct, any useful Matlab functions that are not super-important enough to put in Core (like BLOM_FunctionCode, BLOM_Get<...>, etc). We will probably write scripts for upgrading Simulink models to newer BLOM versions, fixing library links, modifying file formats, etc and should put those here.

Callbacks is for Simulink callbacks that aren't useful enough to be Utils in their own right.

Matrix is for the matrix-valued stuff, if we keep that around.

